%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
\usepackage[document]{ragged2e}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Albert}{Suarez}
\title{Cover letter}                               	% optional, remove / comment the line if not wanted
\phone[mobile]{+34~644~577~607}                   	% optional, remove / comment the line if not wanted
% \phone[fixed]{+2~(345)~678~901}                  	% optional, remove / comment the line if not wanted
% \phone[fax]{+3~(456)~789~012}                    	% optional, remove / comment the line if not wanted
\email{alsumo95@gmail.com}                          % optional, remove / comment the line if not wanted
\homepage{www.asuarez.ga}                         	% optional, remove / comment the line if not wanted
\extrainfo{Software Engineer}                 		% optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

\newcommand{\CompanyPosition}{Biene meme generator}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
\recipient{Recruitment team}{Perth}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}

\makelettertitle

\justify
Please accept my application for the full time position as a \CompanyPosition\space. I am an experienced overseas developer from Spain, and a passionate about computer science.

\justify
After graduating in Software Engineering from the Polytecnic University of Catalonia, I worked as a software developer at UPCnet, Barcelona, a big information technology consulting firm. I performed as a developer programming in different languages like Java, C++, Python, Android and Javascript.

\justify
Afterwards, I had some experience in communication skills as I worked as a teacher at ASES Academy, where my role was teaching two subjects to groups of 20 to 30 people university students, these two were: Data Structures and Algorithms and Operative Systems.

\justify
Finally, my last job in Spain was in the Hackathon world. I am currently working in a student organization as a co director of HackUPC, the first and biggest Hackathon in Spain. This hackathon hosts around 700 participants. My role consists in organizing, managing and coordinating a team of 30 organizers, the event design, logistics, volunteers, sponsorship and marketing.

\justify
I will arrive in Australia on the 26th of October 2017 with Work\&Holiday visa which allows me to work full time, as your position offers.

\justify
Every professional experience has given me skills across a broad range of disciplines, so I am especially committed to the continuous self learning and motivation, and I think I would be a great asset.

\justify
I would love to be part of this incredible staff as you seem to be a leading software organization that would give so much to my engineering career.

\justify
I do hope you will be interested in my application. I would be happy to attend a possible interview at any time, either online or in person upon my arrival in Australia. Should you require further information, please do not hesitate to contact me. I am looking forward to receiving your response in the near future.

\makeletterclosing

\end{document}

%% end of file `template.tex'.